A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-05-01 paper.tex
Added a sentence about the parallel track & unique instances

Our implementation was able to solve 103 out of the 250 specification in the
alloted time, including 12 instances that were not solved by any other
solver in SYNTCOMP'15. The unique instances we solved are listed in
Table~\ref{tab:unique}.

@@

Whilst our solver is unable to solve as many instances as other tools, it was
able to solve more unique instances than any solver in the competition. This
confirms that our methodology is able to fill gaps in a state of the art
synthesis toolbox by more efficiently solving instances that are hard for other
techniques. For this reason our solver would be a worthwhile addition to a
portfolio solver. In the parallel track of the competition, \textsc{Demiurge}
uses a suite of 3 separate but communicating solvers. The solvers
relay unsafe states to one another, which is compatible with the set $B^M$ in
our solver. It remains future work to explore the possibility of combining
these solvers.

>>>>

Our implementation was able to solve 103 out of the 250 specification in the
alloted time, including 12 instances that were not solved by any other solver
in the sequential track of the competition. The unique instances we solved are
listed in Table~\ref{tab:unique}.

@@

Whilst our solver is unable to solve as many instances as other tools, it was
able to solve more unique instances than any solver in the competition. This
confirms that our methodology is able to fill gaps in a state of the art
synthesis toolbox by more efficiently solving instances that are hard for other
techniques. For this reason our solver would be a worthwhile addition to a
portfolio solver. In the parallel track of the competition, \textsc{Demiurge}
uses a suite of 3 separate but communicating solvers. The solvers
relay unsafe states to one another, which is compatible with the set $B^M$ in
our solver. This technique can already solve each of the unique instances
solved by our solver but there may still be value in the addition of this work
to the portfolio.  It remains future work to explore this possibility.
